---
title: "ASTHO’s Profile of State and Territorial Public Health"
subtitle: "Overview of the Nation’s Foremost Data Source on State and Territorial Public Health Infrastructure"
affiliations: []
brand: "brand.yml"
resources: 
  - static
  - images
format:
  html:
    grid:
      margin-width: 75px
      sidebar-width: 235px
    page-layout: article
    theme: [brand, styles.scss, emoji.css]
    embed-resources: true
    self-contained: true
    toc: true
    toc-location: left
    toc-title: Table of Contents
    toc-depth: 3
    number-sections: false
    smooth-scroll: true
    title-block-banner: 'images/profileBannerQuarto.png'
    title-block-categories: true
    fig-responsive: true
    other-links:
      - text: ASTHO website
        href: https://www.astho.org/
      - text: ASTHO Profile Dashboard
        href: https://www.astho.org/profile
      - text: Profile Data | ICPSR page
        href: https://www.icpsr.umich.edu/web/HMCA/studies/39285/summary
      - text: 2025 Profile Survey Instrument
        href: /static/2025_instrument.docx
        icon: filetype-docx
      - text: 2022 codebook
        href: /static/2022_codebook.xlsx
        icon: filetype-xlsx
      - text: 2025 codebook
        href: /static/2025_codebook.xlsx
        icon: filetype-xlsx
---

```{r}
#| echo: false
#| message: false
#| warning: false

library(tibble)
library(tidyverse)
library(dplyr)
library(magrittr)
library(highcharter)
library(fontawesome)
library(stringr)

source("asthoTheme.R")
source("accredPeerNetworkCall_slidoResults.R")


```

# About the Profile {style="text-align: center;"}

------------------------------------------------------------------------

## What is it? {style="text-align: center;"}

::: {style="text-align: left;"}
ASTHO’s Profile survey has gathered information on state, territorial, and freely associated state public health agencies (S/THAs) activities, structure, and resources since 2007.
:::

## How is it used? {style="text-align: center;"}

::: {style="text-align: left;"}
The Profile is the most comprehensive data source about S/THAs in the United States and has many potential applications for public health decision makers, stakeholders, and researchers.
:::

::: {.rounded-box style="text-align: left;"}
-   Advocacy for public health needs
-   Onboarding new public health leaders
-   Trending public health infrastructure
-   Needs assessments and strategic planning
-   National and cross-jurisdiction comparisons
:::

| 
| 

# Relevant Info {style="text-align: center;"}

------------------------------------------------------------------------

::: {style="text-align: left;"}
## Survey

Originally fielded via qualtrics; jurisdicitons were given 2 ways to respond:

-   Full survey
-   Survey broken into individual section links

## Data

-   Data are being validated, cleaned, etc.
-   Historically this has been done in SAS, but we are trying to move away from SAS generally
-   Still finalizing the data set structure and variable naming conventions to be used moving forward

## Dashboard

-   Dashboard is hosted on shinyapps.io
    -   we expect this to change given the sunsetting of shinyapps.io along with the limitations experienced with the platform
    -   posit connect is a potenital option, but would still have limitations around custom domains
    -   ideally would like to get the dahboard back on the main astho website, which might mean iframe embed
        -   might be good to schedule a call with our web team at some point
-   Viz are implemented primarily using highcharts (both via highcharter and API)
-   We use fontawesome icons (have pro access)
:::

| 
| 
| 



# Preliminary Profile Discovery Findings
------------------------------------------------------------------------

## Overall Impression of the Profile

### From Most Negative (1) to Most Postive (5)

```{r}
#| echo: false
#| message: false
#| warning: false
impression

```

## Profile Dashboard Landing Page Reactions

### Wordcloud

```{r}
#| echo: false
#| message: false
#| warning: false
word_cloud_e
```
